---
title: "Todd_Garner_Week4_Part2"
author: "Todd Garner"
date: "2023-01-22"
output: powerpoint_presentation
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# DS6306 Week 4 FLS, Part 2

## FLS Part 2: Freestyle!

1. Install and load one of the packages given in the list for downloading APIs (or another API you have found and are interested in).
>>>>>>>>Initially, I used Intrinio but gave up trying to grab extra data.  I am using WDI and am pulling GDP data from Namibia, Nepal and Niger. 

2. Download data from that API and create a slide that clearly describes the package and how (the code) to download data from that API.  
>>>>>>>>Luckily, R has a function built in that acts as an API with "WDI."  It doesn't require a key or secret key.  I used those when coding in Python and typically put my keys in a .env file which would not translate to GitHub.  This is much easier.  

3. Clearly describe the data and the columns / variables that are of interest to your presentation. 
>>>>>>>>I must admit that I'm basically following your example.  But, I loaded up various GDP codes and selected one that had three " . " in it.  There were numerous lists of data and I picked Namibia, Nepal and Niger.  This contracted starkly against the data pulled from the US, Canada and Mexico.  These are very poor nations.  

4. Perform a small EDA with your data.  Use plots and possibly tests, to find 2 interesting characteristics of the data that you accessed through the API.  
>>>>>>Mainly I varied the time period over which the GDP was measured.  1960-1980 was not that exciting, but the really interesting one was 2000 - 2012 where Namibia's GDP grew at almost 33% over 12 years.  That's very impressive growth.  Nepal and Niger tracked similarly and only moved a fraction of the amount that Namibia did.  

5. Create a PPT presentation to show in the live session.
    a. Show part or all of the data and make sure to show the data are tidy. 
    b. Include at least 1 plot or chart from ggplot.  
    c. You should have no more than five slides (including the title slide).
    d. Include your code. 
    e. Also include a discussion of any obstacles you ran into and went around or over in the process… there will inevitably be one and likely more.  
        >>>>>>>>I could not get the code to print to PPT.  I spent an indordinate amount of time wrestling with this.  I consulted posit.com which solved my issue.  Other issues were the API not working on Intrinio.  I was able to run the code chunks provided but when I went after additional data sets, it completely failed.  I did spend a considerable amount of time on that.  I used to be able to pull data in from Alpaca but that was in Python, which I suppose I could have done, but that seems outside of the goal set out at the start.  I finally punted and used the similar data set from WDI.  Admittedly, this is not my finest work, by far!  I found that I spun my wheels significantly.  But, I did learn quite a bit.  
 

```{r}
# World Bank Development Indicators

#Goal 1: Create a bar chart of topics relating to gdp.
library(WDI)
library(tidyr)
library(tidyverse)
#search for reports with "gdp" in the description
results = as.data.frame(WDIsearch("gdp"))

#This line will filter the data frame to leave only those with 4 pieces in the indicator.
resultsGoodIndicator = results %>% filter(str_count(indicator,"\\.")==3)

#Check out the new data frame with only 4 piece indicators.  This function worked and I deleted the calling of the variable to save space in the PPT. 


# Break the indicator code up into 4 distinct columns. 
resultsGoodIndicator = as.data.frame(resultsGoodIndicator) %>% separate(indicator,c("topic","general","specific","extension"))
head(resultsGoodIndicator)

#compare the expenditure (NE) and the income (NY)
resultsGoodIndicator %>% ggplot(aes(x = topic, fill = extension)) + geom_bar()



#Goal 2: Plot GDP (NY and GDP) per capita (PCAP) of Namibia, Nepal and Niger in constant US dollars (KD)

dat = WDI(indicator='NY.GDP.PCAP.KD', country=c('NE','NP','NA'), start=2000, end=2012)

new_df <- subset(dat, select = -c(iso2c, iso3c))

#I used the str(dat) function to illuminate what the character types were and then proceeded.  

library(ggplot2)
knitr::kable(new_df)
ggplot(new_df, aes(x = year, y = NY.GDP.PCAP.KD, color=country)) + geom_point() + 
  xlab('Year') + ylab('GDP per capita')
```

The plot shows the explosive growth in Namibia in the past 12 years.  


